---
title: "DB_26_Prac"
author: "Shannon Keenan"
date: "10/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
db13 <- read_excel("../data/db13.xls")
View(db13)
```

Here is a header of my data, database 13. This is for observing the differences between lab and clinic readings for Warafin, a blood anticoagulant measured in international normalized ration vlaues. 

```{r}
library(expss)
head(db13)
db13 = apply_labels(db13,
                    clininout = "Clinic Readings",
                    labinout = "Lab Readings")
```
Let's make a table comparing the results of the lab and clinic readings 

```{r}
#readings <- cro(db13$clininout, db13$labinout)
#readings

clinOut <- array(db13$clininout)
labOut <- array(db13$labinout)

#combined <- clinOut + labOut
#length(clinOut)

same_neg = 0
clin_neg_lab0 = 0
clin_neg_lab1 =0 
clin0_labNeg = 0
clin0_lab0 = 0
clin0_lab1 = 0
clin1_labNeg = 0
clin1_lab0 = 0
clin1_lab1 = 0

# print(clinOut)
# print(labOut)
# print(labOut[104])

for (i in 1:length(clinOut)) {
if (clinOut[i] == -1  && labOut[i] == -1) {
    same_neg = same_neg + 1
}    

if (clinOut[i] == -1 && labOut[i] == 0){
    clin_neg_lab0 = clin_neg_lab0 + 1
}
if (clinOut[i] == -1 && labOut[i] == 1){
    clin_neg_lab1 = clin_neg_lab1 + 1
}
if (clinOut[i] == 0 && labOut[i] == -1){
clin0_labNeg = clin0_labNeg + 1
}
if (clinOut[i] == 0 && labOut[i] == 0){
clin0_lab0 = clin0_lab0 + 1
}
if (clinOut[i] == 0 && labOut[i] == 1){
clin0_lab1 = clin0_lab1 + 1
}
if (clinOut[i] == 1 && labOut[i] == -1){
clin1_labNeg = clin1_labNeg + 1
}
if (clinOut[i] == 1 && labOut[i] == 0){
clin1_lab0 = clin1_lab0 + 1
}    
if (clinOut[i] == 1 && labOut[i] == 1){
clin1_lab1 = clin1_lab1 + 1
}
}

all_counts <- c(same_neg,
                clin0_labNeg,
                clin1_labNeg,
clin_neg_lab0,
clin0_lab0,
clin1_lab0,
clin_neg_lab1, 
clin0_lab1,
clin1_lab1)

#all_counts

# print(i)
# print(j)
# print(same_neg)
# print(clin_neg_lab0)
# 
 readings <- matrix(data = all_counts, nrow = 3, ncol = 3)
colnames(readings) = c("-1", "0", "1" )
rownames(readings) =  c( "-1", "0", "1" )
names(dimnames(readings)) <- c("Clinic Readings", "Lab Readings")
 
 readings
```


Let's make a table with the proportions of each :

```{r}
tab2 <- table(db13$clininout, db13$labinout)
tab2
```
Let's run a Chi-Sq test for independence 
#test
```{r}

chisq.test(db13$clininout, db13$labinout)


```
This test is giving us a warning that the approximations may be incorrect. This is because the expected values for each cell were not all greater than 1 and the entries were not all greater than 5. We should not use a Chi- squared test here. Let's use a Fisher's Exact Test. 

```{r}
fisher.test(db13$clininout, db13$labinout)
```
This a very small p-value. This means that the null hypothesis that the column and rows are independent of each other can be rejected.
Let's try a G-test

```{r}
library(pROC)
#View(db1)
#plot.roc(db1$tru, db1$psa)

plot.roc(db18$hsv2, db18$yrshiv)


```

